Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-10-26 doc/references.tex
1st draft complete

@@

@@

\bibitem[\protect\citeauthoryear{Nandra, Lasenby, 
\& Hobson}{2012}]{NandraEtal2012} Nandra R., Lasenby A.~N., Hobson M.~P., 2012, MNRAS, 422, 2945

@@

% \bibitem[\protect\citeauthoryear{Suyu}{2012}]{Suyu2012b} Suyu 
% S.~H., 2012, arXiv, arXiv:1202.0287

>>>>

\bibitem[Cropper et al.(2012)]{EUCLID} Cropper, M., Cole, R., 
James, A., et al.\ 2012, arXiv:1208.3369

@@

\bibitem[LSST Science Collaboration et al.(2009)]{LSST} LSST 
Science Collaboration, Abell, P.~A., Allison, J., et al.\ 2009, 
arXiv:0912.0201

\bibitem[Macci{\`o} et al.(2008)]{MaccioEtal2008} Macci{\`o}, A.~V., 
Dutton, A.~A., \& van den Bosch, F.~C.\ 2008, \mnras, 391, 1940

@@

@@

\bibitem[\protect\citeauthoryear{Suyu}{2012}]{Suyu2012a} Suyu 
S.~H., 2012, arXiv, arXiv:1202.0287
